% -*-latex-*-
% $Log: cover.tex,v $
% Revision 1.7  2001/02/08 18:53:16  boojum
% changed some \newpages to \cleardoublepages
%
% Revision 1.6  1999/10/21 14:49:31  boojum
% changed comment referring to documentstyle
%
% Revision 1.5  1999/10/21 14:39:04  boojum
% *** empty log message ***
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.3  93/05/17  17:06:29  starflt
% Added acknowledgements section (suggested by tompalka)
% 
% Revision 1.2  92/04/22  13:13:13  epeisach
% Fixes for 1991 course 6 requirements
% Phrase "and to grant others the right to do so" has been added to 
% permission clause
% Second copy of abstract is not counted as separate pages so numbering works
% out
% 
% Revision 1.1  92/04/22  13:08:20  epeisach
\title{Composable Probabilistic Inference with \Blaise}

\author{Keith Allen Bonawitz}
\department{Department of Electrical Engineering and Computer Science}
% If the thesis is for two degrees simultaneously, list them both
% separated by \and like this:
% \degree{Doctor of Philosophy \and Master of Science}
\degree{Doctor of Philosophy in Computer Science and Engineering}
\degreemonth{June}
\degreeyear{2008}
\thesisdate{April 30, 2008}

%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
%\copyrightnoticetext{\copyright IBM, 1990.  Do not open till Xmas.}

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Patrick H. Winston}{Ford Professor of Artificial Intelligence and Computer Science}
\supervisor{Joshua B. Tenenbaum}{Paul E. Newton Career Development Professor}

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Arthur C. Smith}{Chairman, Department Committee on Graduate Students}

% Make the titlepage based on the above information.  If you need
% something special and can't use the standard form, you can specify
% the exact text of the titlepage yourself.  Put it in a titlepage
% environment and leave blank lines where you want vertical space.
% The spaces will be adjusted to fill the entire page.  The dotted
% lines for the signatures are made with the \signature command.
\maketitle

% The abstractpage environment sets up everything on the page except
% the text itself.  The title and other header material are put at the
% top of the page, and the supervisors are listed at the bottom.  A
% new page is begun both before and after.  Of course, an abstract may
% be more than one page itself.  If you need more control over the
% format of the page, you can use the abstract environment, which puts
% the word "Abstract" at the beginning and single spaces its text.

%% You can either \input (*not* \include) your abstract file, or you can put
%% the text of the abstract directly between the \begin{abstractpage} and
%% \end{abstractpage} commands.

% First copy: start a new page, and save the page number.
\cleardoublepage
% Uncomment the next line if you do NOT want a page number on your
% abstract and acknowledgments pages.
% \pagestyle{empty}
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{abstract}
\end{abstractpage}

% Additional copy: start a new page, and reset the page number.  This way,
% the second copy of the abstract is not counted as separate pages.
% Uncomment the next 6 lines if you need two copies of the abstract
% page.
% \setcounter{page}{\thesavepage}
% \begin{abstractpage}
% \input{abstract}
% \end{abstractpage}

\cleardoublepage

\section*{Acknowledgments}

This thesis would not have been possible without the help and support of innumerable friends, family
and colleagues.  Let me start by thanking my thesis committee: Patrick Winston, Josh Tenenbaum, and Antonio Torralba.
Patrick has advised me since I was an undergraduate, guiding me through the deep questions of 
artificial intelligence from the perspective of understanding human-level cognition. 
I am also deeply indebted to Patrick for teaching me both
how to frame my ideas and how to present them to others -- without a doubt, Patrick is a master
of this art, and I can only hope I have absorbed some of his skills.  I thank Josh for teaching
me the power of combining probabilistic modeling and symbolic reasoning.
Moreover, I thank Josh for fostering a vibrant and social research environment, both 
inside the lab and out -- there is definitely something wonderful to be said for insightful
conversation while hiking in New Hampshire.  
% I am grateful to Antonio for his feedback and discussion
% while writing this document, and specifically for helping me make the material more accessible.

I cannot praise my community at MIT highly enough.  My friends and colleagues in Patrick's lab,
in Josh's lab, and throughout the Institute have been the most wonderful support system I could 
ask for, not to mention their influence on my thoughts about this work and science in general.
Special thanks to Dan Roy for bravely using a very early version of this work for his own research,
despite its rough edges and lack of documentation, and to Vikash Mansinghka, Beau Cronin, and Eric
Jonas for embracing the ideas in this thesis and providing crucial input and endless encouragement.  

I thank my parents, Lynn and John Bonawitz, for teaching me to follow my dreams with passion
and integrity, and to build the life that works for me.  They and my brother, Michael Bonawitz,
are remarkable in their ability to
always let me know how much I'm loved and missed, while still encouraging my pursuits -- even when those pursuits
take me far away from them.

But most of all, this thesis would never have happened if not for my wife Liz Bonawitz.  Liz's
boundless love and support have been a constant source of strength, encouraging me to be the best
I can be, both personally and professionally, and challenging me to forge my own path and chase both
my ideas and my ideals.  From graduate school
applications through my defense, Liz has been by my side every step of the way -- introducing me to
many of the people and ideas that have become the core of my work, but also making sure I didn't miss
out on the fun and laughter life has to offer. 
% -- even after I accidentally called her Fatty Fat Fat Fatso McFat.  Now that's {\em love!}

\vspace{6.5in}

\begin{singlespace}
This material is based upon work supported by the National Science Foundation 
under Grant No. 0534978. Any opinions, findings, and conclusions or 
recommendations expressed in this material are those of the author(s) and do 
not necessarily reflect the views of the National Science Foundation.
\end{singlespace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% -*-latex-*-
